Interval Probability for Fuzzy Quantum Theories

### 2016-07-24 prob.tex
prob.tex Fix a typo...
prob.tex \subsection{Quantum Probability Measures} Updates...

Based on quantum events are projection operators, operations and properties of
quntum events can be written in terms of those of operators.

@@

A quantum probability measure can be easily constructed by states
according to the Born rule~\cite{Born1983,Mermin2007,RiederSvozil2007}.
For each pure normalized ($\ip{\phi}{\phi}=1$) quantum state $\ket{\phi}$,
the Born rule induces a probability measure $\mu_{\phi}^{B}$ as follows:
\[
\mu_{\phi}^{B}(P)=\ip{\phi}{P\phi}\textrm{ .}
\]

@@

Recall that the Radon-Nikodym theorem claims every probability measure
has an unique Radon-Nikodym derivative with respect to the counting
measure. When we generalize the Radon-Nikodym theorem to quantum,
the mixed state~$\rho$ can be considered as the Radon-Nikodym derivative
with respect to the trace~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007},
and gives Gleason's theorem: in Hilbert spaces of dimension $d\geq3$,
given a quantum probability measure $\mu$, there exist a mixed state~$\rho$
that induces such a measure using the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
By applying Gleason's theorem, we can extend lemma~\ref{lem:quantumProbabilityMeasure}
to the following corollary.

@@

\begin{example}[One-qubit quantum probability measure] Consider
a quantum probability measure~$\mu:\events\rightarrow[0,1]$ defined
as follow: 
\[
\mu(P)=\begin{cases}
1 & \textrm{, if }P=\proj{\ps}\textrm{ ;}\\
0 & \textrm{, if }P=\proj{\ms}\textrm{ ;}\\
\mu^B_{\ket{0}}(P) & \textrm{, otherwise.}
\end{cases}
\]
On one hand, $\mu$ is a quantum probability measure. Because $\mu$ is almost
the same as a quantum probability measure~$\mu^B_{\ket{0}}$, we only
need to check the orthogonal pair~$\proj{\ps}$ and $\proj{\ms}$:
\[
\mu(\proj{\ps})+\mu(\proj{\ms})=1+0=1\textrm{ .}
\]
On the other hand, $\mu$ cannot be induced by any mixed state because
\[
\mu(\proj{\ps})=\mu(\proj{0})=1\textrm{ .}
\]
However, $\mu^B_{\rho}(P)=1$ if and only if $\rho$ represents
a pure state and $\rho=P$. \qed\end{example}

>>>>

Because quantum events are projection operators, operations and properties
of quantum events can be written in terms of those of operators.

@@

Recall that classical probability measure can be constructed from
its Radon-Nikodym derivative. Similarly, a quantum probability measure
can be easily constructed by states according to the Born rule~\cite{Born1983,Mermin2007,RiederSvozil2007}.
For each pure normalized ($\ip{\phi}{\phi}=1$) quantum state $\ket{\phi}$,
the Born rule induces a probability measure $\mu_{\phi}^{B}$ as follows:
\[
\mu_{\phi}^{B}(P)=\ip{\phi}{P\phi}\textrm{ .}
\]

@@

Notice that the mixed state~$\rho$ is really a generalization of
Radon-Nikodym derivative if we pick a basis~$\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$
such that $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\ket{\psi_{j}}\in S}}\proj{\psi_{j}}$,
where $S$ is the linear subspace $P$ projects onto. By representing
the density matrix~$\rho$ in the same basis, i.e., $\rho=\sum_{i=1}^{d}\sum_{j=1}^{d}r_{ij}\ket{\psi_{i}}\bra{\psi_{j}}$,
the Born rule becomes
\begin{eqnarray}
\mu_{\rho}^{B}\left(P\right) & = & \Tr\left(\rho P\right)=\sum_{\ket{\psi_{j}}\in S}r_{jj}\textrm{ ,}\label{BornRule.mixed-1}
\end{eqnarray}
 which is basically the same as equation (\ref{eq:Radon-Nikodym}).

Then, the Radon-Nikodym theorem is generalized quantum~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007}.
If the mixed state~$\rho$ is considered as the Radon-Nikodym derivative
with respect to the trace, we have Gleason's theorem: in Hilbert spaces
of dimension $d\geq3$, given a quantum probability measure $\mu$,
there exist a mixed state~$\rho$ that induces such a measure using
the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
By applying Gleason's theorem, we can extend lemma~\ref{lem:quantumProbabilityMeasure}
to the following corollary.

@@

\begin{example}[One-qubit quantum probability measure] Consider
a quantum probability measure~$\mu:\events\rightarrow[0,1]$ defined
as follow: 
\[
\mu(P)=\begin{cases}
1 & \textrm{, if }P=\proj{\ps}\textrm{ ;}\\
0 & \textrm{, if }P=\proj{\ms}\textrm{ ;}\\
\mu_{\ket{0}}^{B}(P) & \textrm{, otherwise.}
\end{cases}
\]
On one hand, $\mu$ is a quantum probability measure. Because $\mu$
is almost the same as a quantum probability measure~$\mu_{\ket{0}}^{B}$,
we only need to check the orthogonal pair~$\proj{\ps}$ and $\proj{\ms}$:
\[
\mu(\proj{\ps})+\mu(\proj{\ms})=1+0=1\textrm{ .}
\]
On the other hand, $\mu$ cannot be induced by any mixed state because
\[
\mu(\proj{\ps})=\mu(\proj{0})=1\textrm{ ,}
\]
and $\mu_{\rho}^{B}(P)=1$ if and only if $\rho$ represents a pure
state and $\rho=P$. \qed\end{example}
